{\large Gravitational wave sources in our Galactic backyard:}\\{\normalsize Predictions for BHBH, BHNS and NSNS binaries in LISA

### 2021-07-29 paper/tex/paper.tex
floor feedback: abstract
floor feedback: software

\keywords{LISA, gravitational waves, black hole, neutron star, binary}

@@

\software{COMPAS (version 02.12.00) \url{http://github.com/TeamCOMPAS/COMPAS}. \citep{Stevenson+2017, Vigna-Gomez+2018, Broekgaarden+2019}, \texttt{Python} available from \url{python.org}, matplotlib \citep{Hunter+2007},  \texttt{NumPy} \citep{vanderWalt+2011}, 
Astropy \citep[\url{http://www.astropy.org}][]{AstropyCollaboration+2013, AstropyCollaboration+2018}.}

>>>>

\keywords{gravitational waves, LISA, black hole, neutron star, binary}

@@

\software{We used LEGWORK to evolve sources over time and calculate signal-to-noise ratios, it is freely available at \url{https://legwork.readthedocs.io/en/latest/}. Simulations in this paper made use of the COMPAS rapid binary population synthesis code, which is freely available at \url{http://github.com/TeamCOMPAS/COMPAS} \citep{Stevenson+2017, Vigna-Gomez+2018, Broekgaarden+2019}. The simulations performed in this work were simulated with a COMPAS version that predates the publicly available code. Our version of the code is most similar to version 02.13.01 of the publicly available COMPAS code. Requests for the original code can be made to Floor Broekgaarden. The authors used {\sc{STROOPWAFEL}} from \citep{Broekgaarden+2019}, publicly available at \url{https://github.com/FloorBroekgaarden/STROOPWAFEL}\footnote{For the latest pip installable version of STROOPWAFEL please contact Floor Broekgaarden.}.
The authors also made use of Python from the Python Software Foundation. Python Language Reference, version 3.6. Available at \url{http://www.python.org}. In addition the following Python packages were used: matplotlib \citep{Hunter+2007},  {NumPy} \citep{vanderWalt+2011}, SciPy \citep{Virtanen+2020}, Jupyter Lab \citep{Kluyver+2016}, seaborn \citep{Waskom+2020}, h5py \citep{Collette+2021} and Astropy \citep[\url{http://www.astropy.org}][]{AstropyCollaboration+2013, AstropyCollaboration+2018}.  This research has made use of NASA’s Astrophysics Data System Bibliographic Services. We also made use of the computational facilities from the Harvard FAS Research Computing cluster.}
